% Thesis prologue: \include after \begin{document}.

% Title page
\maketitle

% Committee approval page, using the size of committee excluding the advisor.
% Note that "3" is the only supported number!
\makeapproval{3}

% Copyright page (optional)
%\makecopyright
\begin{copyrightpage}
\noindent COPYRIGHT PAGE

\bigskip
The following chapters have been published in peer-reviewed journals. Copyright releases have been obtained from Springer Nature for the publication in \textit{Estuaries and Coasts} and John Wiley and Sons for the publication in \textit{Limnology and Oceanography} for reproduction in this dissertation.

\vspace{2em}
\noindent CHAPTER I

Howard JL, A Perez, CC Lopes, \& JW Fourqurean. (2016). Fertilization changes seagrass community structure but not blue carbon storage: results from a 30-year field experiment. \textit{Estuaries and Coasts}, 39(5), 1422-1434.


\bigskip

\noindent CHAPTER III

Howard JL, JC Creed, MV Aguiar, \& JW Fourqurean. (2017). CO\textsubscript{2} released by carbonate sediment production in some coastal areas may offset the benefits of seagrass “Blue Carbon” storage. \textit{Limnology and Oceanography}, 63(1), 160-1172.

\vspace{3em}

All other materials $\copyright$ Copyright 2018 by Jason L. Howard. All rights reserved.
\end{copyrightpage}

% Dedication page (optional)
%\begin{dedication}
%To my parents.
%\end{dedication}

% Acknowledgments (optional)
\begin{acknowledgments}

\indent This work could not have been completed without the thoughtful academics and hardworking staff that helped me from start to finish; this work is yours as it is mine. First, I’d like to thank my advisor James Fourqurean for welcoming me to the south Florida coastal science community, with its rich history of research. Jim not only gave the freedom of perusing my interests but the resources to do so. He throws his incoming lab members straight into the deep end of Florida Bay and coastal science, and doing so has made me a stronger researcher. My committee members helped guide my development through direct advice as well as setting examples for how good science is conducted. Joel Creed shared his experience, knowledge, and time as if he were an advisor.

Thank you to my labmates: Christian Lopes has been fundamental to the development of this dissertation, from collecting data before the sun came up to discussing ideas through the night. Alex Perez helped me understand the lab’s legacy and the beauty of Florida Bay. Jenn Sweatman welcomed me to the lab and helped me get oriented. Sara Wilson helped me get science done in every possible way. Kai Lopez, David Barahona, and Kaya Carrión helped tremendously on the boat and in the lab, always with jokes and stories.

Thank you to university resources: Mark Kershaw helped maintain instrumentation and taught me to do the same. Jeff Absten and Tom Frankovich facilitated field expeditions and loaned me expensive research instruments. Vicki Absten donated samples, Florida Bay expertise, and arranged logistical support in the Keys. The Key Largo Interagency Science Center was the hub for most of my dissertation field work; it is one of the best resources for FIU coastal research and the study of Florida Bay.

There are a number of researchers who have personally inspired my academic interests and the topics of this dissertation: Sue Kilham, Rui Santos, Heather Stoll, Just Cebrian, Miguel Ángel Mateo, Bart Christiaen, Michael O'Connor, Carlos Duarte, and Steve Thomas.
\end{acknowledgments}

% Abstract
\begin{abstract}
\input{abstract}
\end{abstract}

% Table of Contents
\contentspage

% List of Tables (only if you have 5 or more)
\tablelistpage

% List of Figures (only if you have 5 or more)
\figurelistpage

