\begin{center}
JASON LEE HOWARD \\[4ex]
\end{center}

\noindent EDUCATION \& EXPERIENCE\\[1ex]

\begin{tabular}{ll}

2017-current 	\hspace{1in} & Research fellow, FIU \\[2ex]

2014-2016  & Graduate research assistant, FIU \\[2ex]

2012-2014 	& Graduate teaching assistant, FIU \\[2ex]

2010-2012         & M.S., Marine Biodiversity and Conservation \\
                & Ghent University \\
		& Ghent, Belgium \\[2ex]

2010-2012 & Graduate fellow, European Union \\[2ex]

2010 & Intern, Dauphin Island Sea Lab \\[2ex]

2009 & Research technician, Drexel University \\[2ex]

2006-2008 		& B.S., Biology, minor in Philosophy \\
	        & Drexel University \\
		& Philadelphia, PA \\[2ex]

2005-2006 & Bicycle messenger, independent contractor \\[2ex]

2003-2005            & St. Mary's College \\
                & St. Mary's City, MD  \\[2ex]

\end{tabular}
\\[3.6ex]

\noindent
PUBLICATIONS\\[1ex]

\noindent
Hendriks, IE, YS Olsen, L Ramajo, L Basso, A Steckbauer, TS Moore, JL Howard, and CM Duarte. 2014. Photosynthetic activity buffers ocean acidification in seagrass meadows. {\em Biogeosciences} 11:333–346.\\[1ex]

\noindent
Howard JL, JC Creed, MVP Aguiar, and JW Fourqurean. 2017. CO\textsubscript{2} released by carbonate sediment production in some coastal areas may offset the benefits of seagrass “Blue Carbon” storage. {\em Limnology and Oceanography}, 63(1), 160–172.\\[1ex]

\noindent
Howard JL, A Perez, CC Lopes, and JW Fourqurean. 2016. Fertilization changes seagrass community structure but not Blue Carbon stores: results from a 30-year field experiment. {\em Estuaries and Coasts}, 39(5), 1422-1434.\\[1ex]

\noindent
Zandonà E, SK Auer, SS Kilham, JL Howard, A López-Sepulcre, MP O’Connor, RD Bassar, A Osorio, CM Pringle, and DN Reznick. 2011. Diet quality and prey selectivity correlate with life histories and predation regime in Trinidadian guppies. {\em Functional Ecology}, 25:964–973.\\[2ex]

\noindent
Zandonà E, C Dalton, RW El-Sabaawi, JL Howard, MC Marshall, SS Kilham, DN Reznick, J Travis, TJ Kohler, AS Flecker, SA Thomas, and CM Pringle. 2017. Population variation in the trophic niche of the Trinidadian guppy from different predation regimes. {\em Scientific Reports}. 7:5770\\[1ex]

\noindent
